### 2014-07-16 Paper.tex
added r3c relations

\item[(R3')(a)] For every chordless cycle of the form \begin{tikzpicture}[baseline=-0.5ex]
    \matrix[matrix of math nodes,column sep={25pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
  {
    && |[name = u]|\bullet& \\
    %
    &|[name=dl]| \circ & &|[name=dr]| \circ \\
  };
\draw[->]
  (u) to node[right] {1} (dr)
  ;
  \draw[->]
  (dl) to node[left]{2}(u)
  ;
  \draw[->]
  (dr) to node[below]{2}(dl)
  ;
  \node [yshift = .4 cm] at (u){i};
    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){k};
   \end{tikzpicture}
   we include the three relations
   \begin{enumerate}[(1)]
\item $s_{i}s_{j}^{-1}s_{k}s_{j} = s_{j}^{-1}s_{k}s_{j}s_{i}$
\item $s_{j}s_{k}^{-1}s_{i}s_{k} = s_{k}^{-1}s_{i}s_{k}s_{j}$
\item $s_{k}^{-1}s_{i}^{-1}s_{j}s_{i}s_{k}s_{i}^{-1}s_{j}s_{i}s_{k}^{-1}s_{i}^{-1}s_{j}^{-1}s_{i} = e.$
\end{enumerate}
\end{itemize}
\end{defn}

@@

\begin{lem}
Let $\Gamma$ be a diagram of finite type which contains a chordless cycle C:
\begin{tikzcd}
i_0 \arrow{r} & i_1 \arrow{r} & \cdots \arrow{r} & i_{d-1} \arrow{r} & i_0
\end{tikzcd}
so that all edges have weight 1. Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (R2') and r(i_{a}, i_{a+1}) for some a $\in \{1, \dots, d\}$, all of the relations in (R3)(a) hold for C.
\end{lem}

>>>>

\item[(R3')(b)] For every chordless cycle of the form \begin{tikzpicture}[baseline=-0.5ex]
    \matrix[matrix of math nodes,column sep={25pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
  {
    && |[name = u]|\circ& \\
    %
    &|[name=dl]| \circ & &|[name=dr]| \circ \\
  };
\draw[->]
  (u) to node[right] {1} (dr)
  ;
  \draw[->]
  (dl) to node[left]{2}(u)
  ;
  \draw[->]
  (dr) to node[below]{2}(dl)
  ;
  \node [yshift = .4 cm] at (u){i};
    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){k};
   \end{tikzpicture}
   we include the three relations
   \begin{enumerate}[(1)]
\item $s_{i}s_{j}^{-1}s_{k}s_{j} = s_{j}^{-1}s_{k}s_{j}s_{i}$
\item $s_{j}s_{k}^{-1}s_{i}s_{k} = s_{k}^{-1}s_{i}s_{k}s_{j}$
\item $s_{k}^{-1}s_{i}^{-1}s_{j}s_{i}s_{k}s_{i}^{-1}s_{j}s_{i}s_{k}^{-1}s_{i}^{-1}s_{j}^{-1}s_{i} = e.$
\end{enumerate}
\item[(R3')(c)] For every chordless cycle of the form
\begin{tikzpicture}[baseline=-0.5ex]
    \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
  {
    & |[name = ul]|\circ & |[name = ur]|\circ\\
    %
    &|[name=dl]| \circ &|[name=dr]| \circ \\
  };
\draw[->]
  (ul) to node[above] {1} (ur)
  ;
  \draw[->]
  (dl) to node[left]{2}(ul)
  ;
  \draw[->]
  (dr) to node[below]{1}(dl)
  ;
  \draw[->]
  (ur) to node[right]{2} (dr)
  ;
    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){i};
   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){j};
    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){k};
    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){l};

   we include the two relations
   \begin{enumerate}[(1)]
\item $s_{i}s_{j}^{-1}s_{k}^{-1}s_ls_{k}s_j = s_{j}^{-1}s_{k}^{-1}s_ls_ks_{j}s_{i}$
\item $s_{k}s_{l}^{-1}s_{i}^{-1}s_js_{i}s_l = s_{l}^{-1}s_{i}^{-1}s_js_is_{l}s_{k}$
\end{enumerate}
\end{itemize}
\end{defn}

@@

\begin{lem}
Let $\Gamma$ be a diagram of finite type which contains a chordless cycle C:
\begin{tikzcd}
i_0 \arrow{r} & i_1 \arrow{r} & \cdots \arrow{r} & i_{d-1} \arrow{r} & i_0
\end{tikzcd}
so that all edges have weight 1. Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (R2') and $r(i_{a}, i_{a+1})$ for some a $\in \{1, \dots, d\}$, all of the relations in (R3)(a) hold for C.
\end{lem}
